Put Title here

### 2018-11-26 General WLD combinatorics.tex
fixed the intervals in the first two cases

\begin{proof}
    We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since unsupported vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with no unsupported vertices.  Then by Lemma~\ref{lem sian} $W$ has at least one of the four situations illustrated in figure~\ref{fig 3 cases}

@@

Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.  In this case the support of $p$ is unsupported in $V$ so for every propagator $r$ in $V$ (including $q$) $J_r^{(V)} = J_r^{(W)}$.  Additionally, $J_p^{(W)}(l+t) = l+a$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$ which proves the result in this case.

@@

\textbf{Left two cases}: In both of these cases, $p$ has limited effect on the Grassmann necklace of $W$ due to the presence of at least one previously unsupported vertex $l$.  Let $1\leq a\leq 3$ be the number of unsupported vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.  Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.  Note that $l, \ldots, l+a-1$ are all in the support of $p$.  We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$: if $w\in J_q^{(V)}(i)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{(V)}(i+1)$ or $w\in J_q^{(V)}(j)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
      \]
For the majority of the remaining vertices, we use the following observation: if $p$ is the first propagator to contribute to a Grassmann necklace term $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.  Thus in both cases, we have for any $0\leq b <a$
    \[
    I_{l+b}^{(W)}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b}^{(V)}(r) & \text{if } r\neq p
    \end{cases}
    \]
    If $j$ is in the support of $p$ which occurs in all cases except the second case with two vertices in the right hand region then
     \[
       I_j^{(W)}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
         I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}
       \end{cases}
       \]
       If $j$ is not in the support of $p$, then we must be in the second case with two vertices in the right hand region.  In this case if we start at $j$ we need to know whether propagators other than $p$ will remain around $i$ and $i+1$ when we reach vertex $i$ in the Grassmann necklace algorithm so as to know what $p$ contributes.  Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.  $X$ is still admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.  Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.  Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so starting at $j+1$ and assigning propagators to vertices according to the Grassmann necklace algorithm, when we get to the vertex $i$ in $X$ all propagators other than $q$ must have been assigned.  Starting then at $j$ in $W$ we first assign $q$ to $j$, then proceed to assign as in $X$ starting at $j+1$ and then when we get to $i$ the only propagator left to assign is $j$.  Therefore
       \[
       I_j^{(W)}(p) = m \text{if $j$ is not in the support of $p$}
       \]

For the left two cases of Figure~\ref{fig 3 cases} it remains to consider the starting vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
\[
       I_{j+1}^{(W)}(r)  = \begin{cases}
         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
         I_{j+2}^{(V)}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
       \end{cases}
       \]  Thus if $j+1$ is in the support of $p$ then $m=j-2$, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
       ***these intervals need checking***
\[J^{(W)}_p(j-2) = [j+2,c], \quad J^{(W)}_p(j-1) = [c+1,j-1], \quad J^{(W)}_p(j) = \{j\}, \quad J^{(W)}_p(j+1) = \{j+1\}\]
  where
  \[
  c = \begin{cases} d-1 & \text{if } m=i+1 \\
    j-2 & \text{otherwise}
      \end{cases}
  \]
also satisfies the statement of the theorem.

Now suppose $j+1$ is not in the support of $p$. If we start at $j+1$ we need to know whether any other propagators remain on edge $i$ when we reach vertex $i$. We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.  However the construction of $I^{(V)}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{(V)}_{j+2}$.  In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$. 
    Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
    \[
    I_{j+1}^{(W)}(r)  = \begin{cases}
      m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
      I_{j+1}^{(V)}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
    \end{cases}
    \]
    ***I have to redo assembling the intervals***
    Assembling the intervals, we have
\[J^{(W)}_p(m) = [m+4, ], \quad J^{(W)}_p(m+1) = [j+2,d-1], \quad J^{(W)}_p(m+2) = [d,m+2], \quad J^{(W)}_p(m+3) = \{m+3\},\]
which are nonempty and otherwise as required.

\textbf{Right hand case}: In this case there are no unsupported vertices $l, \ldots$ inside $q$.  Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$. For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        m & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{(V)}(j)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        \max\{m, j+1\} & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]

@@

\begin{align*}
      I_{j+1}^{(W)}(r) &= \begin{cases}
        \max\{j+2, m\} & \text{if } r=p\\
        I_{j+1}^{(V)}(r) & \text{if } r\neq p
      \end{cases}\\
      I_m^{(W)}(r) &= \begin{cases}
        m & \text{if $r=p$ and $q$ not supported on $m$}\\
        m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
        I_{m}^{(V)}(r) & \text{if } r\neq p
      \end{cases}\\
      I_{m+1}^{(W)}(r) & = \begin{cases}
        m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
        m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
        I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
      \end{cases}\\
      I_{m+2}^{(W)}(r) & = \begin{cases}
        m+2 & \text{if } r=p \\
        I_{m+3}^{(V)}(r) & \text{if } r\neq p
      \end{cases}\\
      I_{m+3}^{(W)}(r) & = \begin{cases}
        m+3 & \text{if } r=p \\
        I_{m+4}^{(V)}(r) & \text{if } r\neq p
      \end{cases}
\end{align*}
Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$. Once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$, and
***Fix these intervals again***
\[J_p^{(W)}(c) = [c+4,e-1], \quad J_p^{(W)}(c+1) = [e,c], \quad J_p^{(W)}(c+2) = \{c+1,c+2\}, \quad J_p^{(W)}(c+3) = \{c+3\}.\]

>>>>

\begin{proof}
    We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since unsupported vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with no unsupported vertices.  Then by Lemma~\ref{lem sian} $W$ has at least one of the four situations illustrated in figure~\ref{fig 3 cases}.

@@

Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.  In this case the support of $p$ is unsupported in $V$ so for every propagator $r$ in $V$ (including $q$) $J_r^{(V)} = J_r^{(W)}$.  Additionally, $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$ which proves the result in this case.

@@

\textbf{Left two cases}: In both of these cases, $p$ has limited effect on the Grassmann necklace of $W$ due to the presence of at least one previously unsupported vertex $l$.  Let $1\leq a\leq 3$ be the number of unsupported vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.  Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.  Note that $l, \ldots, l+a-1$ are all in the support of $p$.  We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$: if $w\in J_q^{(V)}(i)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{(V)}(i+1)$ or $w\in J_q^{(V)}(j)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
      \]
For the majority of the remaining vertices, we use the following observation: if $p$ is the first propagator to contribute to a Grassmann necklace term $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.  Thus in both cases, we have for any $0\leq b <a$
    \[
    I_{l+b}^{(W)}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b}^{(V)}(r) & \text{if } r\neq p
    \end{cases}
    \]
    If $j$ is in the support of $p$ which occurs in all cases except the second case with two vertices in the right hand region then
     \[
       I_j^{(W)}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
         I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}
       \end{cases}
       \]
       If $j$ is not in the support of $p$, then we must be in the second case with two vertices in the right hand region.  In this case if we start at $j$ we need to know whether propagators other than $p$ will remain around $i$ and $i+1$ when we reach vertex $i$ in the Grassmann necklace algorithm so as to know what $p$ contributes.  Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.  $X$ is still admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.  Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.  Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so starting at $j+1$ and assigning propagators to vertices according to the Grassmann necklace algorithm, when we get to the vertex $i$ in $X$ all propagators other than $q$ must have been assigned.  Starting then at $j$ in $W$ we first assign $q$ to $j$, then proceed to assign as in $X$ starting at $j+1$ and then when we get to $i$ the only propagator left to assign is $j$.  Therefore
       \[
       I_j^{(W)}(p) = m \text{ if $j$ is not in the support of $p$}
       \]

For the left two cases of Figure~\ref{fig 3 cases} it remains to consider the starting vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
\[
       I_{j+1}^{(W)}(r)  = \begin{cases}
         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
         I_{j+2}^{(V)}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
       \end{cases}
       \]
%Thus if $j+1$ is in the support of $p$ then $m=j-2$, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
%       ***these intervals need checking***
%\[J^{(W)}_p(j-2) = [j+2,c], \quad J^{(W)}_p(j-1) = [c+1,j-1], \quad J^{(W)}_p(j) = \{j\}, \quad J^{(W)}_p(j+1) = \{j+1\}\]
%  where
%  \[
%  c = \begin{cases} d-1 & \text{if } m=i+1 \\
%    j-2 & \text{otherwise}
%      \end{cases}
%  \]
%also satisfies the statement of the theorem.

Now suppose $j+1$ is not in the support of $p$. If we start at $j+1$ we need to know whether any other propagators remain on edge $i$ when we reach vertex $i$. We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.  However the construction of $I^{(V)}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{(V)}_{j+2}$.  In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$. 
    Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
    \[
    I_{j+1}^{(W)}(r)  = \begin{cases}
      m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
      I_{j+1}^{(V)}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
    \end{cases}
    \]

    Taking all the possibilities for the left two cases of Figure~\ref{fig 3 cases}, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
    \begin{itemize}
      \item 
    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
    \[
    J^{(W)}_p(m) = [m+4, m], \quad J^{(W)}_p(m+1) = \{m+1\}, \quad J^{(W)}_p(m+2) = \{m+2\}, \quad J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are nonempty and otherwise as required.
  \item
        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
    \[
    J^{(W)}_p(m) = [m+4, d-1], \quad J^{(W)}_p(m+1) = [d, m+1], \quad J^{(W)}_p(m+2) = \{m+2\}, \quad J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are nonempty and otherwise as required.
  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
    \[
    J^{(W)}_p(m) = \{m+3\}, \quad J^{(W)}_p(m+1) = [m+4, d-1], \quad J^{(W)}_p(m+2) = [d, m+1], \quad J^{(W)}_p(m+3) = \{m+2\},
    \]
    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
    \[
    J^{(W)}_p(m) = [m+4, j+1], \quad J^{(W)}_p(m+1) = [j+2, d-1], \quad J^{(W)}_p(m+2) = [d, m+1], \quad J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are again as required.
    \end{itemize}

\textbf{Third case}: In this case there are no unsupported vertices $l, \ldots$ inside $q$.  Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$. For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        m & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{(V)}(j)$ then
    \[
    I_w^{(W)}(r) =  \begin{cases}
        \max\{m, j+1\} & \text{if } r=p \\
        I_{w}^{(V)}(r) & \text{if } r\neq p
      \end{cases} 
    \]

@@

\begin{align*}
  I_{j+1}^{(W)}(r) &= \begin{cases}
    j+1 & \text{if } r=q\\
    j+2 & \text{if } r=p\\
    I_{j+3}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_m^{(W)}(r) &= \begin{cases}
    m & \text{if $r=p$ and $q$ not supported on $m$}\\
    m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
    I_{m}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+1}^{(W)}(r) & = \begin{cases}
    m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
    m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
    I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_{m+2}^{(W)}(r) & = \begin{cases}
    m+2 & \text{if } r=p \\
    I_{m+3}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+3}^{(W)}(r) & = \begin{cases}
    m+3 & \text{if } r=p \\
    I_{m+4}^{(V)}(r) & \text{if } r\neq p
  \end{cases}
\end{align*}
Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$. Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$.  Assembling the intervals for $p$ we get, and
***I still have to fix these intervals***
\[J_p^{(W)}(c) = [c+4,e-1], \quad J_p^{(W)}(c+1) = [e,c], \quad J_p^{(W)}(c+2) = \{c+1,c+2\}, \quad J_p^{(W)}(c+3) = \{c+3\}.\]
